### 2020-02-05 README.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

# Please put your title here to include it in the file below.
Title <- "Resilience of different technologies towards climate change for Singapore"
```

# resilience

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/resilience/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/resilience/actions)
<!-- badges: end -->

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r
> Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL:
<https://github.com/ideas-lab-nus/resilience/archive/master.zip>

Or you can install this compendium as an R package, resilience, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ideas-lab-nus/resilience")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our
[contributor guidelines](.github/CONTRIBUTING.md). Please note that this project
is released with a [Contributor Code of Conduct](.github/CONDUCT.md). By participating
in this project you agree to abide by its terms.

### 2020-02-05 analysis/transition.R

@@ -1,0 +1,24 @@
+# read the model
+idf <- eplusr::read_idf(here::here("data-raw/model/Singapore_Benchmark_Model.idf"))
+
+# update to v9.1
+idf <- eplusr::transition(idf, 9.1)
+
+# fix validation error
+# 1. equipment list
+id <- unique(idf$validate()$incomplete_extensible$object_id)
+idf$set(.(id) := list(
+    "Zone Equipment 1 Sequential Cooling Fraction" = 1,
+    "Zone Equipment 1 Sequential Heating Fraction" = 1
+))
+# 2. autosize
+val <- idf$validate()$invalid_autosize[
+    , list(id = object_id, class = class_name, index = field_index, value = value_chr)][
+    , value := "Autocalculate"]
+idf$update(val)
+
+# 3. geometry rules
+idf$GlobalGeometryRules$set("UpperLeftCorner", "Counterclockwise")
+
+# save
+idf$save(here::here("data/idf/Singapore_Benchmark_Model.idf"), overwrite = TRUE)

### 2020-02-05 README.Rmd
[docs] Rename project-wide
# |<----  Using a Maximum Of 50 Characters  ---->|


# Explain why this change is being made
# |<----   Try To Limit Each Line to a Maximum Of 72 Characters   ---->|

# Provide links or keys to any relevant tickets, articles or other resources
# Example: Github issue #23

# --- COMMIT END ---
# Type can be 
#    feat (new feature)
#    fix (bug fix)
#    docs (changes to documentation)
#    style (formatting, missing semi colons, etc; no code change)
#    refactor (refactoring production code)
#    test (adding missing tests, refactoring tests; no production code cha

@@
 # Please put your title here to include it in the file below.
-Title <- "Resilience of different technologies towards climate change for Singapore"
+Title <- "An R-based framework for conducting parametric analysis on building energy models"
 ```
 
-# resilience
+# eplusr + epluspar
 
 <!-- badges: start -->
-[![R build status](https://github.com/ideas-lab-nus/resilience/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/resilience/actions)
+[![R build status](https://github.com/ideas-lab-nus/epluspar-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/epluspar-paper/actions)
 <!-- badges: end -->
@@
 You can download the compendium as a zip from from this URL:
-<https://github.com/ideas-lab-nus/resilience/archive/master.zip>
+<https://github.com/ideas-lab-nus/epluspar-paper/archive/master.zip>
 
-Or you can install this compendium as an R package, resilience, from GitHub with:
+Or you can install this compendium as an R package, epluspar-paper, from GitHub with:
 
@@
 # install.packages("remotes")
-remotes::install_github("ideas-lab-nus/resilience")
+remotes::install_github("ideas-lab-nus/epluspar-paper")
 ```

### 2020-05-22 analysis/transition.R
[style] Remove redundant files copied from project template

@@ -1,24 +1,0 @@
-# read the model
-idf <- eplusr::read_idf(here::here("data-raw/model/Singapore_Benchmark_Model.idf"))
-
-# update to v9.1
-idf <- eplusr::transition(idf, 9.1)
-
-# fix validation error
-# 1. equipment list
-id <- unique(idf$validate()$incomplete_extensible$object_id)
-idf$set(.(id) := list(
-    "Zone Equipment 1 Sequential Cooling Fraction" = 1,
-    "Zone Equipment 1 Sequential Heating Fraction" = 1
-))
-# 2. autosize
-val <- idf$validate()$invalid_autosize[
-    , list(id = object_id, class = class_name, index = field_index, value = value_chr)][
-    , value := "Autocalculate"]
-idf$update(val)
-
-# 3. geometry rules
-idf$GlobalGeometryRules$set("UpperLeftCorner", "Counterclockwise")
-
-# save
-idf$save(here::here("data/idf/Singapore_Benchmark_Model.idf"), overwrite = TRUE)

### 2020-05-29 README.Rmd
[docs] Update README

@@
 # Please put your title here to include it in the file below.
-Title <- "An R-based framework for conducting parametric analysis on building energy models"
+Title <- "A framework for integrating building energy simulation and data-driven analytics"
+Author <- "Hongyuan Jia and Adrian Chong"
+Journal <- "Energy and Buildings"
 ```
 
-# eplusr + epluspar
+# eplusr framework
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>
+> `r Author`, (2020). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> `r Author`, (2020). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r
-> Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at
-> <https://doi.org/xxx/xxx>
+> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
 ### How to download or install
+
+**(a) Option 1: Download the compiled draft PDF**
+
+The latest compiled draft PDF can be downloaded from the `Artifacts`.
+
+```{r, echo = FALSE}
+knitr::include_graphics(here::here("figures/artifact.png"))
+```
+
+**(b) Option 2: Download the compendium and compile the PDF**
 
@@
 remotes::install_github("ideas-lab-nus/epluspar-paper")
+```
+
+The PDF can be compiled via:
+
+```{r, eval = FALSE}
+rmarkdown::render('vignettes/paper.Rmd')
 ```

### 2020-05-29 README.Rmd
[docs] Fix figure path in README
[docs] Tweak figure output width
[docs] Complete repo renaming

@@
 <!-- badges: start -->
-[![R build status](https://github.com/ideas-lab-nus/epluspar-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/epluspar-paper/actions)
+[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
 <!-- badges: end -->
@@
 
-```{r, echo = FALSE}
-knitr::include_graphics(here::here("figures/artifact.png"))
+```{r, echo = FALSE, out.width = "30%"}
+knitr::include_graphics("figures/artifact.png")
 ```
@@
 You can download the compendium as a zip from from this URL:
-<https://github.com/ideas-lab-nus/epluspar-paper/archive/master.zip>
+<https://github.com/ideas-lab-nus/eplusr-paper/archive/master.zip>
 
-Or you can install this compendium as an R package, epluspar-paper, from GitHub with:
+Or you can install this compendium as an R package, eplusr-paper, from GitHub with:
 
@@
 # install.packages("remotes")
-remotes::install_github("ideas-lab-nus/epluspar-paper")
+remotes::install_github("ideas-lab-nus/eplusr-paper")
 ```

### 2020-07-05 README.Rmd
[docs] Update README

@@
 
-This repository contains the data and code for our paper:
+This repository contains the data and code for paper:
 
-> `r Author`, (2020). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>
-
-Our pre-print is online here:
-
-> `r Author`, (2020). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> `r Author`, (2020). _`r Title`_. (In review)
 
@@
 
-> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.
 
@@
 
-The latest compiled draft PDF can be downloaded from the `Artifacts`.
-
-```{r, echo = FALSE, out.width = "30%"}
-knitr::include_graphics("figures/artifact.png")
-```
+The latest compiled draft PDF can be downloaded from the `Actions` &#8594; `Artifacts`.
 

### 2020-07-05 README.Rmd
[docs] Update build badge in README [skip-ci]

@@
 <!-- badges: start -->
-[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
+[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/eplusr-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
 <!-- badges: end -->
